PragBat Analysis

### 2022-04-07 analysis/analysis.Rmd
add model based reliability file

  model <- brm(correct ~  z_age + (0+test_day|id),
            data = data%>%filter(study == "study1", task == i), 
            family = bernoulli(),
          #control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          #save_all_pars = TRUE,
          iter = 2000)

@@

  model <- brm(correct ~  z_age + (0+test_day|id),
            data = data%>%filter(study == "study2", task == i), 
            family = bernoulli(),
          #control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          #save_all_pars = TRUE,
          iter = 2000)

>>>>

  model <- brm(correct ~  z_age + (0+test_day|id),
            data = data%>%filter(study == "study1", task == i), 
            family = bernoulli(),
          #control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          #save_all_pars = TRUE,
          iter = 4000)

@@

  model <- brm(correct ~  z_age + (0+test_day|id),
            data = data%>%filter(study == "study2", task == i), 
            family = bernoulli(),
          #control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          #save_all_pars = TRUE,
          iter = 4000)
